Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-28 disc.tex
[draft] wording changes for descritive text.

In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.

>>>>

In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the replacement recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.

### 2017-06-28 general_formulation.tex
[draft] wording changes for descritive text.

Despite the general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are however many successful attempts to construct a subset of those bosonic boundary states. Rather than Virasoro generator, one may use current operator which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989}. This idea has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Further, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which begins with a classical boundary condition and the boundary state follows from the quantization. The interface obtained is actually the same as the one from using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but the scattering process derived here is more intuitive and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} is more transparent.

@@

The boundary state expression in Eq.~\eqref{eq:bd_state} will be used extensively in fidelity and Loschmidt echo calculation in Sec.~\ref{sec:analytic_numerics}.

>>>>

Although general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states. For example, one may use the current operator rather than the Virasoro generator to solve the zero momentum flow condition. This idea dates back to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Additionally, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state. The interface obtained is actually the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.

@@

The boundary state expression in Eq.~\eqref{eq:bd_state} will be used extensively in the fidelity and Loschmidt echo calculation in Sec.~\ref{sec:analytic_numerics}.

### 2017-06-28 intro.tex
[draft] wording changes for descritive text.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process. Fidelity is the (square of) the overlap of the ground state wavefunctions of the Hamiltonians before and after the quench. There is no dynamic information in fidelity; nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic for the Loschmidt echo computation. The Loschmidt echo is (square of) the overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit. Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. In this paper we extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.

>>>>

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
We compute the Loschmidt echo to extract information in the dynamics of the quench process. The Loschmidt echo is the (square of) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. It decays with a power law $t^{- \alpha}$for the lack of length scale in the $t \rightarrow \infty$ limit. The decay exponent $\alpha$ has been calculated for various geometries and combinations of the normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs. We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transition coefficients. Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. The finite size fidelity calculation further supports these results.
